High-throughput Genomic Paper Notes

### 2017-10-26 Paper_notes/Paper_notes.Rmd
Added summaries for Bolstad et al., 2003 and Cleveland & Devlin, (1988)

---
title: "High-throughput Genomic Paper Notes"
author: "Jonathan Yu"
date: "October 16, 2017"
output: pdf_document
---

@@

>>>>

---
title: "High-throughput Genomic Paper Notes"
author: "Jonathan Yu"
date: "October 25, 2017"
output: pdf_document
---

@@

### Bolstad et al., 2003

- Bolstad, B. M., R. A. Irizarry, M. Astrand, and T. P. Speed. “A Comparison of Normalization Methods for High Density Oligonucleotide Array Data Based on Variance and Bias.” Bioinformatics (Oxford, England) 19, no. 2 (January 22, 2003): 185–93. - Normalization methods description.

Three complete data methods: cyclic loes, contrasted based method, and quantile normalization are different norminalization techniques to reduce obscuring variation between oligonucleotide arrays. Current methods - scaling and non-linear method - utilized by Affymetrix do not reduce the variation as much as the other methods and performed poorly for spike-in regressions. Affymetrix methods do not deal with cases that are non-linear relationships between arrays. The cyclic loess and contrast based method are derived from the M vs A method and could be time consuming. All these methods depend on choice of baselines but the complete data methods performed matter on the matter of variance reduction and bias.

### Cleveland & Devlin, 1988

- Cleveland, William S, and Susan J Devlin. “Locally Weighted Regression: An Approach to Regression Analysis by Local Fitting.” Journal of the American Statistical Association 83, no. 403 (1988): 596–610. - Loess regression. Concept, statistics.

Locally weighted regression (loess) is introduced as a local fitting regression, similar to the least squares, that can be used for data exploration, diagnostic checking  of parametric models and nonparametric regression surface. The dependent variable is smoothed as a function of the independent variable in a moving fashion. They show that this can be used to graph smooth surfaces to help choose a parametric model if needed during the exploratory phase. They then show that the adequacy of the parametric model chosen. Finally, it can be shown that the estimate can be used instead of parametric estimates. The multivariate smoother is an extension of the univariate loess smoother where they use the euclidian distance on each scaled independent variables. Loess is comprised of the weights and the neighborhood size. The M plot can help choose the fraction of points in the neighborhood. Assumption include that the loess estimate be a linear combinaton of the outcome observations, that the outcome is a normal distribution, and the loess estimate is not biased.
